\textcolor{red}{Simple} connectome inference using partial correlation from imaging calcium signal

### 2014-06-16 article.tex
wording in experiments

>>>>

At first sight, it appears on \textit{Table 1} that partial correlation methods outperform other methods. Two main reasons may explain this method hierarchy.
First, the quality of the infered network seems related to the conditioning part of the method. In every method except with partial correlation, indirect links are confounded with direct links. 
Secondly, the gaussian assumption seems verified and thus linear method appears to be competitive, e.g. the method correlation already gives good results, with a non-linear method such as GENIE3.

% Discussion about
